\documentclass[a4paper, 12pt, openany]{book}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[main=english]{babel}

\title{About a CMS}
\author{IsilinBN}
\date{11/06/2016}


\pagestyle{headings}
\setlength{\parindent}{2cm}
\usepackage[top=0cm]{geometry}

\begin{document}
\maketitle
\tableofcontents
\frontmatter
\chapter{Preface}
\chapter{Introduction}
\section{Situation}
\paragraph{}
Between early-June 2015 and end-May 2016, I have begun to develop a PHP framework to help me to produce web applications using a MVC architecture. This framework knew two versions. First was named IsilinMVC and was a naive implementation. The second, named IsilinSAs, was a little more realistic.
I have had the opportunity to use each version for some projects. And this permit me to do feedbacks on my project and what I really want.
\paragraph{}
Now, I\rq{}m becoming an internship in mobile application development in Australia. In an other side, I wish to do a website to write my life during this summer and to broadcast photos taken.
This is the starting point to properly begin my project. The website, will be a crash test for what I develop.
\mainmatter
\part{Goals of the projet}
\chapter{CMS}
\section{Features}
\chapter{Framework}
Target : the web applications
Architecture : MVC, Ajax, multi-architecture ?
RESTful
Allow adds-on
\section{MVC}
\subsection{Models}
\subsection{View}
\subsection{Controller}
\section{API Rest}
\chapter{Environment of development}
\section{Project management}
\subsection{Continuous integration \& continuous deployment}
\subsection{Task management}
\subsection{Network}
\section{Tools}
\subsection{Choice}
\paragraph{Version controle}
Git has been chosen as the version controle system.
It will be used throw the git shell terminal, and connected to a repository stored on a Github server.
\paragraph{Task management}
To manage the task, and the goals, an account on Freedcamp, has been created.
This is a try.
\subsection{Toolchain}
\paragraph{About}
It could be interesting to find a way to automatize the use of each tools.
\part{Phases of the project}
\chapter{Phase 1 - Of development}
\chapter{Phase 2 - Of interface}
\chapter{Phase 3 - Of improvement}
\backmatter
\chapter{Conclusion}
\end{document}